Early Observations of the Type Ia Supernova \abc:\\ \textbf{a Case of Interaction with Nearby, Unbound Material and/or} Strong Ejecta Mixing

### 2017-11-20 doc/ms.tex
minor figure caption clean up

In this paper, we report observations of an extraordinarily young SN Ia, \abc,
which was discovered by the intermediate Palomar Transient Factory (iPTF) on
2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$,
$\textrm{Dec.}=+13\degr51\arcmin14\farcs3$ (J2000) with a
$g_\mathrm{PTF}$-band magnitude of $21.44\pm0.25$ \citep{2016ATel.8907....1M}.
The transient is spatially coincident with a tidal tail of the galaxy
NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected
to a 5-$\sigma$ limit of $g_\mathrm{PTF}=21.9$\,mag on April $2.42$, less than
1\,d prior to discovery, and rose by $\sim$2\,mag in the 24\,hr following its
initial detection. Our spectroscopic follow-up campaign classified \abc\ as a
normal SN Ia \citep{2016ATel.8909....1C}. Our observations and analysis show
that the early evolution of \abc\ exhibited several distinct properties
relative to SN\,2011fe. We interpret those differences as arising from either
strong $^{56}$Ni mixing or ejecta interaction with \textbf{nearby, unbound}
material, or a combination of the two. Alongside this paper, we have released
our open source analysis and all of the data utilized in this study. These are
available online at \texttt{GitHub}
\url{https://github.com/adamamiller/iPTF16abc}.

@@

\begin{figure}[htb] 
    \centering
    \includegraphics[width=3.35in]{logLC_with_colors.pdf} 
    \caption{
    %
    The $g$-band light curve of \abc, with 5-$\sigma$ upper limits shown as
    downward arrows. Observations from different telescopes are shown with
    different symbols. The lower axis shows time measured in rest-frame days
    relative to $t_0$ (see \S\ref{sec:lc_fit}), while the upper axis shows
    time relative to $B$-band maximum. Note that the horizontal axis is shown
    with a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$
    and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. \textbf{Vertical}
    black ticks show epochs of spectroscopic observations. }
% 
    \label{fig:lightcurve} 
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=3.35in]{lightcurve.pdf}
  \caption{
  %
  UV, optical, and NIR light curves for \abc. \textit{Top}: $BVgri$ light
  curves from the P48, P60, LCO-1m, and \textit{Swift} telescopes. The solid
  lines represent the best-fit model from SALT2 (see
  \S\ref{sec:classification}). \textit{Bottom}: UV and NIR light curves from
  the \textit{Swift} and SPM-1.5m telescopes, respectively. For both panels
  each light curve is represented with a different color, while the different
  symbols correspond to different instruments, as detailed in the legends. The
  legends also list offsets applied to each light curve. Photometry is shown
  in the AB mag system, with the exception of the $BV$ bands, which are shown
  in the Vega system. These \textbf{light curves have} not been corrected for
  line-of-sight extinction.}
  %
  \label{fig:ugly_LC}
\end{figure}

>>>>

In this paper, we report observations of an extraordinarily young SN Ia, \abc,
which was discovered by the intermediate Palomar Transient Factory (iPTF) on
2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$,
$\textrm{Dec.}=+13\degr51\arcmin14\farcs3$ (J2000) with a
$g_\mathrm{PTF}$-band magnitude of $21.44\pm0.25$ \citep{2016ATel.8907....1M}.
The transient is spatially coincident with a tidal tail of the galaxy
NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected
\textbf{to a 5-$\sigma$ limit of} $g_\mathrm{PTF}=21.9$\,mag on April $2.42$,
less than 1\,d prior to discovery, and rose by $\sim$2\,mag in the 24\,hr
following its initial detection. Our spectroscopic follow-up campaign
classified \abc\ as a normal SN Ia \citep{2016ATel.8909....1C}. Our
observations and analysis show that the early evolution of \abc\ exhibited
several distinct properties relative to SN\,2011fe. We interpret those
differences as arising from either strong $^{56}$Ni mixing or ejecta
interaction with \textbf{nearby, unbound} material, or a combination of the
two. Alongside this paper, we have released our open source analysis and all
of the data utilized in this study. These are available online at
\texttt{GitHub} \url{https://github.com/adamamiller/iPTF16abc}.

@@

\begin{figure}[htb] 
    \centering
    \includegraphics[width=3.35in]{logLC_with_colors.pdf} 
    \caption{
    %
    The $g$-band light curve of \abc, with 5-$\sigma$ upper limits shown as
    downward arrows. Observations from different telescopes are shown with
    different symbols. \textbf{The lower axis shows time} measured in
    rest-frame days relative to $t_0$ (see \S\ref{sec:lc_fit}), \textbf{while
    the upper axis shows time relative to $B$-band maximum.} Note that the
    horizontal axis is shown with a linear scale for $-2 \; \mathrm{d} \le t -
    t_0 \le 3 \; \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \;
    \mathrm{d}$. \textbf{Vertical} black ticks show epochs of spectroscopic
    observations. }
% 
    \label{fig:lightcurve} 
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=7in]{lightcurve2.pdf}
  \caption{
  %
  UV, optical, and NIR light curves for \abc. \textit{Left}: $BVgri$ light
  curves from the P48, P60, LCO-1m, \textit{Swift}, and SPM-1.5m telescopes.
  The solid lines represent the best-fit model from SALT2 (see
  \S\ref{sec:classification}). \textit{Right}: UV and NIR light curves from
  the \textit{Swift} and SPM-1.5m telescopes, respectively. For both panels
  each light curve is represented with a different color, while the different
  symbols correspond to different instruments, as detailed in the legends. The
  legends also list offsets applied to each light curve. Photometry is shown
  in the AB mag system, with the exception of the $BV$ bands, which are shown
  in the Vega system. These \textbf{light curves have} not been corrected for
  line-of-sight extinction.}
  %
  \label{fig:ugly_LC}
\end{figure}
